Clustering time series based on probability distributions across temporal granularities

### 2021-11-01 main.Rmd
Discussion: future work

There are few areas to extend this research. Firstly, things become far more complicated when we consider a larger data set with more uncertainty, as they do with any clustering problem. Characterising clusters with varied or outlying customers can result in a shape that does not represent the group. Furthermore, combining hetergeneous customers may result in similar-looking final clusters that are not effective for visually differentiating them. Hence, a method for appropriately scaling it up to many customers such that anomalies can be removed before implementing the clustering method, would be useful for bringing out meaningful, compact and separated groups.

Secondly, we have assumed the time series to be stationary and hence the distributions are assumed to remaining constant for the observation period. In reality however, it might change. For the smart meter example, the distribution for a customer moving to a different house or changing electrical equipments can change drastically. These dynamic changes can not be picked up by our method.

Thirdly, it is possible that for few customers, data for some categories from the list of significant granularities are missing. In our application, we have removed those customers and done the analysis but the metrics used should be able to incorporate those customers in the clustering by handling their missing categories.

$wpd$ is computationally heavy even under parallel computation. Future work can make the computations more efficient so that it is easily scalable to a large number of customers.

>>>>

\noindent There are few areas to extend this research. First, larger data sets with more uncertainty complicate matters, as is true for any clustering task. Characterising clusters with varied or outlying customers can result in a shape that does not represent the group. Moreover, integrating heterogeneous consumers may result in visually identical end clusters, which are potentially not useful. Hence, a way of appropriately scaling it up to many customers such that anomalies are removed before clustering would be useful for bringing forth meaningful, compact and separated clusters.

\noindent Secondly, we have assumed the time series to be stationary, and hence the distributions are assumed to remain constant for the observation period. In reality, however, it might change. For the smart meter example, the distribution for a customer moving to a different house or changing electrical equipments can change drastically. Our current approach can not detect these dynamic changes.

\noindent Thirdly, it is possible that for few customers, data for some categories from the list of considered significant granularities are missing. In our application, we have removed those customers and done the analysis but the metrics used should be able to incorporate those customers in the clustering by handling their missing categories.

\noindent Finally, $wpd$ is computationally heavy even under parallel computation. Future work can make the computations more efficient so that they are easily scalable to a large number of customers.
